---
title: "PurgingAnalysis"
author: "somo"
date: "5/7/2019"
output: html_document
---
Comparing the effect of selfing using three schemes. 1) Self, 2) NoSelf, and 3)
Selfmean.  The founder size used is 600 and marker density for genotyping is
1200 The experiment was performed 24 times/replicates/seasons. The gene action
model was of dominance type. The scheme was for five generations. The scripts
for simulations are stored in folder Scheme and partly labelled standard.
NOTE: There is a 25th group which are the means of the 24 replicates. To make
figures, this 25th group needs to be removed
NOTE: Somo and Jean-Luc have a different file structure. Set forSomo <- TRUE
to run analyses on Somo's file structure
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
forSomo <- FALSE
prefix <- ifelse(forSomo, "~/Documents/purgingscenarios/SimulationScripts2019/Schemes/", "~/Google Drive/Teaching/People/MohamedSomoIbrahim/PurgeSimulations/PurgingSimulationScript2019/Schemes/Outputs/")
SelfMean <- readRDS(paste(prefix, "_purgeG2000H1000M1200Q300N500F600NORRANStandard_MeanSelfPlotOut.rds", sep=""))$plotData
Self <- readRDS(paste(prefix, "_purgeG2000H1000M1200Q300N500F600NORRANStandard_SelfPlotOut.rds", sep=""))$plotData
NoSelf <- readRDS(paste(prefix, "_purgeG2000H1000M1200Q300N500F600NORRANStandard_NoSelfPlotOut.rds", sep=""))$plotData
schemeMeans <- cbind(popID=0:5, selfMean=subset(SelfMean, group == 25)$g, self=subset(Self, group == 25)$g, noSelf=subset(NoSelf, group == 25)$g)
SelfMean <- subset(SelfMean, group < 25)
Self <- subset(Self, group < 25)
NoSelf <- subset(NoSelf, group < 25)
```

In this section I am adding a new column as identify before combining the
three data sets. The column is named scheme.
```{r}
SelfMean$scheme <- rep("S1", nrow(SelfMean)) # make new column
Self$scheme <- rep("S2", nrow(Self)) # make new column
NoSelf$scheme <- rep("S3", nrow(NoSelf)) # make new column
Selfmean_Self_NoSelf <- rbind(SelfMean, Self, NoSelf)
table(Selfmean_Self_NoSelf$scheme)
head(Selfmean_Self_NoSelf)
```

Here am extracting generation five data and also excluding the mean of each
scheme. This new data then is used for fitting the model to compare whether
there is significant difference betwen the groups and 
Here the group represent 24 replicates, scheme represents SelfMean, Self, 
and NoSelf, g represent the genetic improvement
```{r}
Selfmean_Self_NoSelf$group <- paste("Rep", Selfmean_Self_NoSelf$group, sep = "")
SchemeGen5dataAnova <- subset(Selfmean_Self_NoSelf, popID == 5)
gen5dataLM <- lm(g ~ 1 + group + scheme,  data=SchemeGen5dataAnova)
# summary(gen5dataLM)
anova(gen5dataLM)
dim(gen5dataLM)
```

```{r}
library(plotrix)
mdfunc<-function(x, na.rm=T){return(sd(x, na.rm=T) / sqrt(sum(!is.na(x))))
}

par(mar = c(4,4,3,2))
bp <- brkdn.plot(g ~ scheme + popID, data=Selfmean_Self_NoSelf, stagger=0.01, ylim=c(-0.1, 1.2), lwd=2, cex=1, col=c("blue", "orange", "black"), md="mdfunc", xlab="Generation", ylab="Genetic Improvement", main="Standard Schemes")
legend("topleft", legend=c("Self", "Self+", "NoSelf"), col=c("orange", "blue","black" ), lwd=2, cex=0.7, horiz = T)

```


FounderSize200
Here I am reading the RDS data and extracting plotdata component from from the plotdata file which has two main data type. I excluded totcost because cost factor was not simulated for
```{r}
prefix <- ifelse(forSomo, "~/Documents/purgingscenarios/SimulationScripts2019/FounderSizes/", "~/Google Drive/Teaching/People/MohamedSomoIbrahim/PurgeSimulations/PurgingSimulationScript2019/FounderSizes/Outputs/")
SelfMean200 <- readRDS(paste(prefix, "_purgeG2000H1000M1200Q300N500F200NORRANFounderSize200_MeanSelfPlotOut.rds", sep=""))$plotData
Self200 <- readRDS(paste(prefix, "_purgeG2000H1000M1200Q300N500F200NORRANFounderSize200_SelfPlotOut.rds", sep=""))$plotData
NoSelf200 <- readRDS(paste(prefix, "_purgeG2000H1000M1200Q300N500F200NORRANFounderSize200_NoSelfPlotOut.rds", sep=""))$plotData

schemeMeans200 <- cbind(popID=0:5, selfMean=subset(SelfMean200, group == 25)$g, self=subset(Self200, group == 25)$g, noSelf=subset(NoSelf200, group == 25)$g)
SelfMean200 <- subset(SelfMean200, group < 25)
Self200 <- subset(Self200, group < 25)
NoSelf200 <- subset(NoSelf200, group < 25)

SelfMean200$scheme <- "S1"
Self200$scheme <- "S2"
NoSelf200$scheme <- "S3" 

FounderSize200<- rbind(SelfMean200, Self200, NoSelf200)

FounderSize200$Founder <- "F200"
head(FounderSize200)
```

FounderSize600
```{r}
prefix <- ifelse(forSomo, "~/Documents/purgingscenarios/SimulationScripts2019/Schemes/", "~/Google Drive/Teaching/People/MohamedSomoIbrahim/PurgeSimulations/PurgingSimulationScript2019/Schemes/Outputs/")
SelfMean600 <- readRDS(paste(prefix, "_purgeG2000H1000M1200Q300N500F600NORRANStandard_MeanSelfPlotOut.rds", sep=""))$plotData
Self600 <- readRDS(paste(prefix, "_purgeG2000H1000M1200Q300N500F600NORRANStandard_SelfPlotOut.rds", sep=""))$plotData
NoSelf600 <- readRDS(paste(prefix, "_purgeG2000H1000M1200Q300N500F600NORRANStandard_NoSelfPlotOut.rds", sep=""))$plotData

schemeMeans600 <- cbind(popID=0:5, selfMean=subset(SelfMean600, group == 25)$g, self=subset(Self600, group == 25)$g, noSelf=subset(NoSelf600, group == 25)$g)
SelfMean600 <- subset(SelfMean600, group < 25)
Self600 <- subset(Self600, group < 25)
NoSelf600 <- subset(NoSelf600, group < 25)

SelfMean600$scheme <- "S1"
Self600$scheme <- "S2"
NoSelf600$scheme <- "S3" 

FounderSize600 <- rbind(SelfMean600, Self600, NoSelf600)

FounderSize600$Founder <- "F600"
head(FounderSize600)
```


FounderSize1500
```{r}
prefix <- ifelse(forSomo, "~/Documents/purgingscenarios/SimulationScripts2019/FounderSizes/", "~/Google Drive/Teaching/People/MohamedSomoIbrahim/PurgeSimulations/PurgingSimulationScript2019/FounderSizes/Outputs/")
SelfMean1500 <- readRDS(paste(prefix, "_purgeG2000H1000M1200Q300N500F1500NORRANFounderSize1500_MeanSelfPlotOut.rds", sep=""))$plotData
Self1500 <- readRDS(paste(prefix, "_purgeG2000H1000M1200Q300N500F1500NORRANFounderSize1500_SelfPlotOut.rds", sep=""))$plotData
NoSelf1500 <- readRDS(paste(prefix, "_purgeG2000H1000M1200Q300N500F1500NORRANFounderSize1500_NoSelfPlotOut.rds", sep=""))$plotData

schemeMeans1500 <- cbind(popID=0:5, selfMean=subset(SelfMean1500, group == 25)$g, self=subset(Self1500, group == 25)$g, noSelf=subset(NoSelf1500, group == 25)$g)
SelfMean1500 <- subset(SelfMean1500, group < 25)
Self1500 <- subset(Self1500, group < 25)
NoSelf1500 <- subset(NoSelf1500, group < 25)

SelfMean1500$scheme <- "S1"
Self1500$scheme <- "S2"
NoSelf1500$scheme <- "S3" 

FounderSize1500<- rbind(SelfMean1500, Self1500, NoSelf1500)

FounderSize1500$Founder <- "F1500"
head(FounderSize1500)
```

Combining all the founders
```{r}
AllFounders <- rbind(FounderSize200, FounderSize600, FounderSize1500)
table(AllFounders$Founder)
```

here am extracting generation five data and also excluding the mean of each scheme. This new data then is used for fitting the model 
to compare whether there is significant difference betwen the groups and 
```{r}
AllFoundersAnova <- subset(AllFounders, popID %in% 5)
Newgen5founderdata<- subset(AllFoundersAnova, group!=25)
Newgen5founderdata$group <- as.character(Newgen5founderdata$group)
str(Newgen5founderdata)
```

Here the group represent 24 replicates, scheme represents SelfMean, Self, and NoSelf, g represent the genetic improvement
```{r}
gen5dataLMFounder <- lm(g~1 + scheme + Founder + group + scheme*Founder + group*Founder, data = Newgen5founderdata)
#summary(gen5dataLMFounder )
anova(gen5dataLMFounder )
dim(gen5dataLMFounder )

```

Plot for all founder sizes
```{r}
FounderSize200NoMean <- subset(FounderSize200, group!=25)
FounderSize600NoMean <- subset(FounderSize600, group!=25)
FounderSize1500NoMean <- subset(FounderSize1500, group!=25)


library(plotrix)
mdfunc<-function(x, na.rm=T){return(sd(x, na.rm=T) / sqrt(sum(!is.na(x))))
}

ylim <- range(c(schemeMeans200[,-1], schemeMeans600[,-1], schemeMeans1500[,-1])) # Extreme of the means
ylim <- ylim + c(-0.1, 0.1) # Make space for the error bars
#par(mfrow=c(3,1))
par(mar = c(4,4,3,2))
bp <- brkdn.plot(g ~ scheme + popID, data=FounderSize200NoMean, ylim=ylim, stagger=0.01, lwd=2,cex=1,col=c("blue", "orange", "black"), md="mdfunc", xlab="Generation", ylab="Genetic Improvement",main="200 Founders")
  legend("topleft",legend=c("Self", "Self+", "NoSelf"), col=c("orange", "blue", "black"), lwd = 2, cex=0.7, horiz = T)
  
bp <- brkdn.plot(g ~ scheme + popID, data=FounderSize600NoMean, ylim=ylim, stagger=0.01, lwd=2,cex=1,col=c("blue", "orange", "black"), md="mdfunc", xlab="Generation", ylab="Genetic Improvement",main="600 Founders")
  legend("topleft",legend=c("Self", "Self+", "NoSelf"), col=c("orange", "blue", "black"), lwd = 2, cex=0.7, horiz = T)
  
bp <- brkdn.plot(g ~ scheme + popID, data=FounderSize1500NoMean , ylim=ylim, stagger=0.01, lwd=2,cex=1,col=c("blue", "orange", "black"), md="mdfunc", xlab="Generation", ylab="Genetic Improvement", main="1500 Founders")
legend("topleft",legend=c("Self", "Self+", "NoSelf"), col=c("orange", "blue", "black" ), lwd = 2, cex=0.7, horiz = T)
```

Equal Contribution
Compare standard to when you reduce inbreeding depression by forcing equal
contribution among parents
```{r}
prefix <- ifelse(forSomo, "~/Documents/purgingscenarios/SimulationScripts2019/Schemes/", "~/Google Drive/Teaching/People/MohamedSomoIbrahim/PurgeSimulations/PurgingSimulationScript2019/Schemes/Outputs/")
notEqSelf <- readRDS(paste(prefix, "_purgeG2000H1000M1200Q300N500F600NORRANStandard_SelfPlotOut.rds", sep=""))$plotData
notEqSelfMean <- readRDS(paste(prefix, "_purgeG2000H1000M1200Q300N500F600NORRANStandard_MeanSelfPlotOut.rds", sep=""))$plotData

schemeMeans1200 <- cbind(popID=0:5, self=subset(marker1200Self, group == 25)$g, noSelf=subset(marker1200NoSelf, group == 25)$g)

marker1200Self <- subset(marker1200Self, group < 25)
marker1200NoSelf <- subset(marker1200NoSelf, group < 25)

marker1200Self$scheme <- "S4"
marker1200NoSelf$scheme <- "S1"

MarkerDensity1200<- rbind(marker1200Self, marker1200NoSelf)
MarkerDensity1200$MarkerDensity<- "MD1200"
head(MarkerDensity1200)
```

MarkerDensity: for 1200 vs 3600 on Self vs NoSelf. Here reading in and extracting the plotdata. For the 1200 marker, I used the standard simulation
data from scheme folder
```{r}
prefix <- ifelse(forSomo, "~/Documents/purgingscenarios/SimulationScripts2019/Schemes/", "~/Google Drive/Teaching/People/MohamedSomoIbrahim/PurgeSimulations/PurgingSimulationScript2019/Schemes/Outputs/")
marker1200Self <- readRDS(paste(prefix, "_purgeG2000H1000M1200Q300N500F600NORRANStandard_SelfPlotOut.rds", sep=""))$plotData
marker1200NoSelf <- readRDS(paste(prefix, "_purgeG2000H1000M1200Q300N500F600NORRANStandard_NoSelfPlotOut.rds", sep=""))$plotData

schemeMeans1200 <- cbind(popID=0:5, self=subset(marker1200Self, group == 25)$g, noSelf=subset(marker1200NoSelf, group == 25)$g)

marker1200Self <- subset(marker1200Self, group < 25)
marker1200NoSelf <- subset(marker1200NoSelf, group < 25)

marker1200Self$scheme <- "S4"
marker1200NoSelf$scheme <- "S1"

MarkerDensity1200<- rbind(marker1200Self, marker1200NoSelf)
MarkerDensity1200$MarkerDensity<- "MD1200"
head(MarkerDensity1200)
```


3600 on Self vs NoSelf
```{r}
prefix <- ifelse(forSomo, "~/Documents/purgingscenarios/SimulationScripts2019/MarkerDensity/", "~/Google Drive/Teaching/People/MohamedSomoIbrahim/PurgeSimulations/PurgingSimulationScript2019/MarkerDensity/Outputs/")
marker3600Self <- readRDS(paste(prefix, "_purgeG2000H1000M3600Q300N500F600NORRANStd_MarkerDensity3600_SelfPlotOut.rds", sep=""))$plotData
marker3600NoSelf <- readRDS(paste(prefix, "_purgeG2000H1000M3600Q300N500F600NORRANStd_MarkerDensity3600_NoSelfPlotOut.rds", sep=""))$plotData

schemeMeans3600 <- cbind(popID=0:5, self=subset(marker3600Self, group == 25)$g, noSelf=subset(marker3600NoSelf, group == 25)$g)

marker3600Self <- subset(marker3600Self, group < 25)
marker3600NoSelf <- subset(marker3600NoSelf, group < 25)

marker3600Self$scheme <- "S2"
marker3600NoSelf$scheme <- "S3"

MarkerDensity3600<- rbind(marker3600Self, marker3600NoSelf)
MarkerDensity3600$MarkerDensity<- "MD3600"
head(MarkerDensity3600)
```

Combining all the founders
```{r}
AllMarkerDensity <- rbind(MarkerDensity1200, MarkerDensity3600)
table(AllMarkerDensity$MarkerDensity)
table(AllMarkerDensity$scheme)
```

Extract generation five data and also excluding the mean of each scheme. This 
new data then is used for fitting the model to compare whether there is
significant difference betwen the groups and 
```{r}
AllMarkerDensityAnova <- subset(AllMarkerDensity , popID%in%5)
Newgen5MarkerDensitydata<- subset(AllMarkerDensity, group!=25)
Newgen5MarkerDensitydata$group <- as.character(Newgen5MarkerDensitydata$group)
```

Here the group represent 24 replicates, scheme represents SelfMean, Self, and 
NoSelf, g represent the genetic improvement
```{r}
gen5dataMdensity <- lm(g ~ 1 + group + MarkerDensity + scheme  + scheme*MarkerDensity + group*MarkerDensity, data = Newgen5MarkerDensitydata)
#summary(gen5dataMdensity)
anova(gen5dataMdensity)
```

```{r}
MarkerDensity1200NoMean <- subset(MarkerDensity1200, group!=25)
MarkerDensity3600NoMean <- subset(MarkerDensity3600, group!=25)

library(plotrix)
mdfunc <- function(x, na.rm=T){return(sd(x, na.rm=T) / sqrt(sum(!is.na(x))))
}

par(mar = c(6,4,4,2))
par(mfrow=c(1, 2))
bpMd1200<-brkdn.plot(g ~ scheme + popID, data=MarkerDensity1200NoMean, ylim = c(-0.3, 1.2), lwd=2,cex=1,col=c("black", "orange"), md="mdfunc", xlab="Generation", ylab="Genetic Improvement", main="MarkerDensity1200")
legend("topleft",legend=c("Self", "NoSelf"), col=c("orange", "black"), lwd = 2, cex=0.7, horiz = T)
  
  
bMd3600<-brkdn.plot(g ~ scheme + popID, data=MarkerDensity3600NoMean , ylim = c(-0.3, 1.2), lwd=2,cex=1,col=c("orange", "black"), md="mdfunc", xlab="Generation", ylab="Genetic Improvement", main="MarkerDensity3600")
legend("topleft",legend=c("Self", "NoSelf"), col=c("orange", "black"), lwd = 2, cex=0.7, horiz = T)
  
par(mfrow=c(1, 1))
allMarkDens <- rbind(MarkerDensity1200NoMean, MarkerDensity3600NoMean)
bp <- brkdn.plot(g ~ scheme + popID, data=allMarkDens, ylim = c(-0.3, 1.2), stagger=0.01, lwd=2, cex=1,col=c("black", "blue", "dark green", "orange"), md="mdfunc", xlab="Generation", ylab="Genetic Improvement", main="Marker Density")
legend("topleft",legend=c("Self 1200", "NoSelf 1200", "Self 3600", "NoSelf 3600"), col=c("orange", "black", "blue", "dark green"), lwd = 2, cex=0.7, horiz = T)
```

program size based on progenies evaluated at CET vs PYT trial types
LESSLESS
```{r}
LessLessSM <- readRDS("~/Documents/purgingscenarios/SimulationScripts2019/ProgramSizeCET:PYT/LessLess/_purgeG2000H1000M1200Q300N500F600NORRANProgramSizeMoreCETLessPYT_MeanSelfPlotOut.rds")
LessLessS <- readRDS("~/Documents/purgingscenarios/SimulationScripts2019/ProgramSizeCET:PYT/LessLess/_purgeG2000H1000M1200Q300N500F600NORRANProgramSizeLessCETLessPYT_SelfPlotOut.rds")
LessLessNS <- readRDS("~/Documents/purgingscenarios/SimulationScripts2019/ProgramSizeCET:PYT/LessLess/_purgeG2000H1000M1200Q300N500F600NORRANProgramSizeLessCETLessPYT_NoSelfPlotOut.rds")
LessLessSMplotdata <- LessLessSM$plotData
LessLessSplotdata <- LessLessS$plotData
LessLessNSplotdata <-LessLessNS$plotData
dim(LessLessSMplotdata)
LessLessSMplotdata$scheme <- rep("SelfMean",nrow(LessLessSMplotdata)); LessLessSplotdata$scheme <- rep("Self", nrow(LessLessSplotdata)); LessLessNSplotdata$scheme <- rep("NoSelf", nrow(LessLessNSplotdata)) 

AllLessLess<- rbind(LessLessSMplotdata, LessLessSplotdata, LessLessNSplotdata)
AllLessLess$Program <- rep("LessLess",nrow(AllLessLess))

AllLessLessNoMean <- subset(AllLessLess, group!=25)

```


LessMore
```{r}
LessMoreSM <- readRDS("~/Documents/purgingscenarios/SimulationScripts2019/ProgramSizeCET:PYT/LessMore/_purgeG2000H1000M1200Q300N500F600NORRANStandard_MeanSelfPlotOut.rds")
LessMoreS <- readRDS("~/Documents/purgingscenarios/SimulationScripts2019/ProgramSizeCET:PYT/LessMore/_purgeG2000H1000M1200Q300N500F600NORRANStandard_SelfPlotOut.rds")
LessMoreNS <- readRDS("~/Documents/purgingscenarios/SimulationScripts2019/ProgramSizeCET:PYT/LessMore/_purgeG2000H1000M1200Q300N500F600NORRANStandard_NoSelfPlotOut.rds")
LessMoreSMplotdata <- LessMoreSM$plotData
LessMoreSplotdata <- LessMoreS$plotData
LessMoreNSplotdata <-LessMoreNS$plotData

LessMoreSMplotdata$scheme <- rep("SelfMean",nrow(LessMoreSMplotdata))
LessMoreSplotdata$scheme <- rep("Self", nrow(LessMoreSplotdata))
LessMoreNSplotdata$scheme <- rep("NoSelf", nrow(LessMoreNSplotdata)) 

AllLessMore<- rbind(LessMoreSMplotdata, LessMoreSplotdata, LessMoreNSplotdata)
AllLessMore$Program <- rep("LessMore",nrow(AllLessMore))
head(AllLessMore)

AllLessMoreNoMean <- subset(AllLessMore, group!=25)
head(AllLessMoreNoMean)
```


MOREMORE
```{r}
MoreMoreSM <- readRDS("~/Documents/purgingscenarios/SimulationScripts2019/ProgramSizeCET:PYT/MoreMore/_purgeG2000H1000M1200Q300N500F600NORRANProgramSizeMoreCETMorePYT_MeanSelfPlotOut.rds")
MoreMoreS <- readRDS("~/Documents/purgingscenarios/SimulationScripts2019/ProgramSizeCET:PYT/MoreMore/_purgeG2000H1000M1200Q300N500F600NORRANProgramSizeMoreCETMorePYT_SelfPlotOut.rds")
MoreMoreNS <- readRDS("~/Documents/purgingscenarios/SimulationScripts2019/ProgramSizeCET:PYT/MoreMore/_purgeG2000H1000M1200Q300N500F600NORRANProgramSizeMoreCETMorePYT_NoSelfPlotOut.rds")
MoreMoreSMplotdata <- MoreMoreSM$plotData
MoreMoreSplotdata <- MoreMoreS$plotData
MoreMoreNSplotdata <-MoreMoreNS$plotData


MoreMoreSMplotdata$scheme <- rep("SelfMean",nrow(MoreMoreSMplotdata))
MoreMoreSplotdata$scheme <- rep("Self", nrow(MoreMoreSplotdata))
MoreMoreNSplotdata$scheme <- rep("NoSelf", nrow(MoreMoreNSplotdata)) 

AllMoreMore<- rbind(MoreMoreSMplotdata, MoreMoreSplotdata, MoreMoreNSplotdata)

AllMoreMore$Program <- rep("MoreMore",nrow(AllMoreMore))
head(AllMoreMore)
table(AllMoreMore$scheme)
AllMoreMoreNoMean <- subset(AllMoreMore, group!=25)
```

MoreLess
```{r}
MoreLessSM <- readRDS("~/Documents/purgingscenarios/SimulationScripts2019/ProgramSizeCET:PYT/MoreLess/_purgeG2000H1000M1200Q300N500F600NORRANProgramSizeMoreCETLessPYT_MeanSelfPlotOut.rds")
MoreLessS <- readRDS("~/Documents/purgingscenarios/SimulationScripts2019/ProgramSizeCET:PYT/MoreLess/_purgeG2000H1000M1200Q300N500F600NORRANProgramSizeMoreCETLessPYT_SelfPlotOut.rds")
MoreLessNS <- readRDS("~/Documents/purgingscenarios/SimulationScripts2019/ProgramSizeCET:PYT/MoreLess/_purgeG2000H1000M1200Q300N500F600NORRANProgramSizeMoreCETLessPYT_NoSelfPlotOut.rds")
MoreLessSMplotdata <- MoreLessSM$plotData
MoreLessSplotdata <- MoreLessS$plotData
MoreLessNSplotdata <-MoreLessNS$plotData


MoreLessSMplotdata$scheme <- rep("SelfMean",nrow(MoreLessSMplotdata))
MoreLessSplotdata$scheme <- rep("Self", nrow(MoreLessSplotdata))
MoreLessNSplotdata$scheme <- rep("NoSelf", nrow(MoreLessNSplotdata)) 

AllMoreLess<- rbind(MoreLessSMplotdata, MoreLessSplotdata, MoreLessNSplotdata)

AllMoreLess$Program <- rep("MoreLess",nrow(AllMoreLess))
head(AllMoreLess)
AllMoreLessNoMean <- subset(AllMoreLess, group!=25)
```


```{r}
library(plotrix)
mdfunc<-function(x, na.rm=T){return(sd(x, na.rm=T) / sqrt(sum(!is.na(x))))
}
par(mar = c(4,5.5,2,1))
 
 par(mfrow=c(2,2))

bp <- brkdn.plot(g~ scheme + factor(popID), data=AllLessLessNoMean,ylim = c(0, 1.3), lwd=2,cex=1, col=c("black", "orange", "blue"),md="mdfunc",
                 lty=1:8, pch=1:8, xlab="Generation", ylab="Genetic Improvement",main="LessLess")
  legend("topleft",legend=c("Self+", "Self", "NoSelf"), col=c("blue","orange","black" ),lty=2, lwd = 2, cex=0.5, horiz = T)
  
bp <- brkdn.plot(g~ scheme + factor(popID), data=AllLessMoreNoMean,ylim = c(0, 1.3), lwd=2,cex=1, col=c("black", "orange", "blue"),md="mdfunc",
                 lty=1:8, pch=1:8, xlab="Generation", ylab="Genetic Improvement",main="LessMore")
legend("topleft",legend=c("Self+", "Self", "NoSelf"), col=c("blue","orange","black"),lty=2, lwd = 2, cex=0.5, horiz = T)


    bp <- brkdn.plot(g~ scheme + factor(popID), data=AllMoreLessNoMean,ylim = c(0, 1.3), lwd=2,cex=1, col=c("black", "orange", "blue"),md="mdfunc",
                 lty=1:8, pch=1:8, xlab="Generation", ylab="Genetic Improvement",main="MoreLess")
  legend("topleft",legend=c("Self+", "Self", "NoSelf"), col=c("blue","orange","black"),lty=2, lwd = 2, cex=0.5, horiz = T)
  
bp <- brkdn.plot(g~ scheme + factor(popID), data=AllMoreMoreNoMean,ylim = c(0, 1.3), lwd=2,cex=1, col=c("black", "orange", "blue"),md="mdfunc",
                 lty=1:8, pch=1:8, xlab="Generation", ylab="Genetic Improvement",main="MoreMore")
  legend("topleft", legend=c("Self+", "Self", "NoSelf"), col=c("blue","orange","black"),lty=2, lwd = 2, cex=0.5, horiz = T)
  
  

  
```

Anova for the Program size. The mean data for each simulation has already been excluded
```{r}
ProgramSize <- rbind(AllLessLessNoMean,AllLessMoreNoMean,AllMoreMoreNoMean,AllMoreLessNoMean)
table(ProgramSize$Program)
head(ProgramSize)
```


Here the group represent 24 replicates, scheme represents SelfMean, Self, and NoSelf, g represent the genetic improvement. The data used for Anova is for generation 5
```{r}


ProgramSizeAnova <- subset(ProgramSize, popID%in%5)
ProgramSizeAnova$group <- as.character(ProgramSizeAnova$group)

gen5dataLMprogramsize <- lm(g~1 + group + scheme    + Program + group*Program + scheme*Program +group*scheme,  data = ProgramSizeAnova)
summary(gen5dataLMprogramsize)
anova(gen5dataLMprogramsize )

```

High and Low Selection Intensity
```{r}
prefix <- ifelse(forSomo, "~/Documents/purgingscenarios/SimulationScripts2019/SelectionIntensity/", "~/Google Drive/Teaching/People/MohamedSomoIbrahim/PurgeSimulations/PurgingSimulationScript2019/SelectionIntensity/Outputs/")
HselectionIntenSM <- readRDS(paste(prefix, "_purgeG2000H1000M1200Q300N500F600NORRANHighSelectionIntensityF600_MeanSelfPlotOut.rds", sep=""))$plotData
HselectionIntenS <- readRDS(paste(prefix, "_purgeG2000H1000M1200Q300N500F600NORRANHighSelectionIntensityF600_SelfPlotOut.rds", sep=""))$plotData
HselectionIntenNS <- readRDS(paste(prefix, "_purgeG2000H1000M1200Q300N500F600NORRANHighSelectionIntensityF600_NoSelfPlotOut.rds", sep=""))$plotData

schemeMeansHigh <- cbind(popID=0:5, selfMean=subset(HselectionIntenSM, group == 25)$g, self=subset(HselectionIntenS, group == 25)$g, noSelf=subset(HselectionIntenNS, group == 25)$g)

HselectionIntenSM$scheme <- "S1"
HselectionIntenS$scheme <- "S2"
HselectionIntenNS$scheme <- "S3" 

AllHighSelectInten<- rbind(HselectionIntenSM, HselectionIntenS, HselectionIntenNS)

AllHighSelectInten$Selection<- rep("HighIntensity",nrow(AllHighSelectInten))

AllHighSelectIntenNoMean <- subset(AllHighSelectInten, group!=25)

```



```{r}
prefix <- ifelse(forSomo, "~/Documents/purgingscenarios/SimulationScripts2019/Schemes/", "~/Google Drive/Teaching/People/MohamedSomoIbrahim/PurgeSimulations/PurgingSimulationScript2019/Schemes/Outputs/")
LselectionIntenSM <- readRDS(paste(prefix, "_purgeG2000H1000M1200Q300N500F600NORRANStandard_MeanSelfPlotOut.rds", sep=""))$plotData
LselectionIntenS <- readRDS(paste(prefix, "_purgeG2000H1000M1200Q300N500F600NORRANStandard_SelfPlotOut.rds", sep=""))$plotData
LselectionIntenNS <- readRDS(paste(prefix, "_purgeG2000H1000M1200Q300N500F600NORRANStandard_NoSelfPlotOut.rds", sep=""))$plotData

schemeMeansLow <- cbind(popID=0:5, selfMean=subset(LselectionIntenSM, group == 25)$g, self=subset(LselectionIntenS, group == 25)$g, noSelf=subset(LselectionIntenNS, group == 25)$g)

LselectionIntenSM$scheme <- "S1"
LselectionIntenS$scheme <- "S2"
LselectionIntenNS$scheme <- "S3" 

AllLowSelectInten<- rbind(LselectionIntenSM, LselectionIntenS, LselectionIntenNS)

AllLowSelectInten$Selection<- "LowIntensity"

AllLowSelectIntenNoMean <- subset(AllLowSelectInten, group!=25)
```


```{r}
library(plotrix)
mdfunc<-function(x, na.rm=T){return(sd(x, na.rm=T) / sqrt(sum(!is.na(x))))
}

ylim <- range(c(schemeMeansLow[,-1], schemeMeansHigh[,-1])) # Extreme of the means
ylim <- ylim + c(-0.1, 0.1) # Make space for the error bars

par(mar = c(4,5.5,2,0))
par(mfrow=c(1,2))

bp <- brkdn.plot(g~ scheme + factor(popID), data=AllHighSelectIntenNoMean,ylim = ylim, lwd=2,cex=1, col=c("blue", "orange", "black"),md="mdfunc", xlab="Generation", ylab="Genetic Improvement",main="High Sel. Intensity (5%)")
legend("topleft",legend=c("Self+", "Self", "NoSelf"), col=c("blue","orange","black" ), lwd = 2, cex=0.5, horiz = T)
  
bp <- brkdn.plot(g~ scheme + factor(popID), data=AllLowSelectIntenNoMean,ylim = ylim, lwd=2,cex=1, col=c("blue", "orange", "black"),md="mdfunc", xlab="Generation", ylab="Genetic Improvement",main="Low Sel. Intensity (10%)")
legend("topleft",legend=c("Self+", "Self", "NoSelf"), col=c("blue","orange","black"), lwd = 2, cex=0.5, horiz = T)
```

Addditive model and foundersizes
```{r}
AdditiveF200 <- readRDS("~/Documents/purgingscenarios/SimulationScripts2019/AdditiveModel/_purgeG2000H1000M1200Q300N500F200NORRANAdditiveModelFounder200SelfPlotOut.rds")$plotData
AdditiveF600 <- readRDS("~/Documents/purgingscenarios/SimulationScripts2019/AdditiveModel/_purgeG2000H1000M1200Q300N500F600NORRANAdditiveModelFounder600SelfPlotOut.rds")$plotData
AdditiveF1500 <- readRDS("~/Documents/purgingscenarios/SimulationScripts2019/AdditiveModel/_purgeG2000H1000M1200Q300N500F1500NORRANAdditiveModelFounder1500SelfPlotOut.rds")$plotData

AllAdditiveMM3 <- subset(AdditiveF200, group!=25)
AllAdditiveMM2 <- subset(AdditiveF600, group!=25)
AllAdditiveMM1 <- subset(AdditiveF1500, group!=25)

```

```{r}
AllAdditiveMM3$Founder <- rep("ADDF200",nrow(AllAdditiveMM3))
AllAdditiveMM2$Founder <- rep("ADDF600",nrow(AllAdditiveMM2))
AllAdditiveMM1$Founder <- rep("ADD1500",nrow(AllAdditiveMM1))


ALlADDFounder <- rbind(AllAdditiveMM1, AllAdditiveMM2,AllAdditiveMM3)
dim(ALlADDFounder)
table(ALlADDFounder$Founder)

data <- lm(g~1 + scheme + Founder + scheme*Founder ,  data = ALlADDFounder)
summary(data)
anova(data )
```

the data is arranged in 1500, 200 and 600 format. The calling for graph follow that order
```{r}
library(plotrix)
mdfunc<-function(x, na.rm=T){return(2*sd(x, na.rm=T) / sqrt(sum(!is.na(x))))
}

par(mar = c(4,5.5,2,0))
 
bp <- brkdn.plot(g~ Founder + popID, data=ALlADDFounder,ylim = c(-0.6, 5), lwd=2,cex=1, col=c("brown","orange", "blue"),md="mdfunc",
                xlab="Generation", ylab="Genetic Improvement",main="Founder|Additive")


  legend("topleft",legend=c("ADD200","ADDF600", "ADDF1500"), col=c("orange", "blue","brown"),lty=2, lwd = 2, cex=0.5, horiz = T)
  
```

See "MainVsPurgeGains.R" for this analysis
Main Selection versus Purging Selection
Here I am using function on 24 reps for substracting between popID with each 
MainSelecSelecSelf600. The same applies to the purgeselection.
```{r Gains from Main vs Purge selection}
library(BreedingSchemeLanguage)

forSomo <- FALSE
prefix <- ifelse(forSomo, "~/Documents/purgingscenarios/SimulationScripts2019/Schemes/", "~/Documents/TooBigForGD/purgeOutput/")
allOutfiles <- list.files(paste(prefix, "AllOut", sep=""))
for (aof in allOutfiles){

  fileName <- paste(prefix, "AllOut/", aof, sep="")
  mainPurge <- readRDS(fileName)
  
  if (exists("simEnv")){
    rm(list=names(simEnv), envir=simEnv)
    rm(simEnv)
  }
  simEnv <- new.env()
  simEnv$sims <- mainPurge
  simEnv$nSim <- length(mainPurge)
  simEnv$nCore <- 1
  mv <- plotData(popID = list(0:1, 1, c(4:5, 13, 19), 5, c(8:9, 18), 9, c(12,14), 14, c(17,20), 20))
  pv <- plotData(popID = list(2:3, 3, 6:7, 7, 10:11, 11, 15:16, 16, 21:22, 22))
  saveRDS(list(mainVals=mv$data, purgeVals=pv$data), file=paste(prefix, "MainPurge/data", aof, sep=""))
  rm(list=setdiff(ls(), c("prefix", "forSomo", "allOutFiles"))); gc()
}

```

```{r}
mainselectionSelfF600 <- Self600Main_Purge
mainselectionSelfF600 <- 
mainselectionSelfF600 <- mainselectionSelfF600$data
mainselectionSelfF600<- subset(mainselectionSelfF600, group!=25)
```


```{r}
Gainvec<-c()
for (i in seq(1, nrow(mainselectionSelfF600)-1, by=2)){
  gainout<-mainselectionSelfF600[i+1,]$g-mainselectionSelfF600[i,]$g
  print(gainout)
  Gainvec<-c(Gainvec,gainout)
}

rep(Gainvec, each=2)#rep for making sure the substracted value appear for both popID (in both rows)
mainselectionSelfF600$diffs<-rep(Gainvec, each=2)
mainselectionSelfF600$diffnames<-rep(names(Gainvec), each=2)
```


```{r}

#plot(Mainselection$g, type="l")
boxplot(mainselectionSelfF600$diffs[(1:length(mainselectionSelfF600$diffs))%%2==1])#Here I am removing the repeat diff.value
mean(mainselectionSelfF600$diffs[(1:length(mainselectionSelfF600$diffs))%%2==1])
sd(mainselectionSelfF600$diffs[(1:length(mainselectionSelfF600$diffs))%%2==1])
```

